### 2020-05-15 Report/aws_325ghz_study.tex
updated text for cloud correction, fixed few typos

Figure~\ref{fig:correction:c34-42:thinned} shows the results when the filtered cloudy cases are corrected. Various metrics from the corrected measurements are also shown in Table~\ref{tab:correction:stats}. When cloudy measurements are filtered with noise-threshold = 1$\sigma$, around 14\% cases of the thinned dataset are classified as corrected and the average deviation in the corrected dataset is -0.069 K. Whereas, with noise-threshold= 2$\sigma$, only 9\% are classfied as cloudy and the average deviation is -0.117 K. This indicates that a larger value of noise threshold can incorrectly classify some cloudy cases as clear.

\begin{table}[!bt]
	\centering
	\begin{tabular}[b]{c|c|c|c}
		 Dataset & Bias & Standard & Measure\\
		 		 & [K] & deviation[K] & skewness [K]\\	
		\hline
		noise & 0.006& 0.628& -0.006\\
		all& -0.818& 4.699& -10.385\\
		thinned& -0.465& 1.556& -5.007\\
		$1\sigma$& -0.069& 0.904& -2.543\\
		$2\sigma$& -0.117& 0.903& -2.597\\
		sreerekha& -0.181& 0.731& -0.506\\
		\hline
	\end{tabular}
	\caption{Various metrics for different subsets of the measurement dataset. The different datasets are: noise(simulation dataset),  All (all measurements are considered), thinned (50\% of clear sky measurements are removed), $1\sigma$ (cloudy measurements are filtered with noise-index = 1$\sigma$), $2\sigma$ (cloudy measurements are filtered with noise-index = 2$\sigma$), sreerekha (measurements are filtered according to criteria described in \cite{rekha2012potential})   }
	\label{tab:correction:stats}
\end{table}
%
In past, \cite{rekha2012potential} have highlighted the applicability of 229 GHz channel to identify the ice clouds. In the report, they use 229 GHz (channel-4x) to identify the ice clouds in 183.31$\pm$7 GHz. In their approach, all cases with TB difference between 229 Ghz and 183.31$\pm$7 GHz greater than 4 K as classified as cloudy. This information can be used to filter out the cloudy cases in all other 183 GHz channels. No correction is provided to the cloudy cases. In order to compare the performance of the correction scheme described here, the filtering scheme by \cite{rekha2012potential} is used a reference. The results from approach are also shown in Figure\ref{fig:correction} and Table~\ref{tab:correction:stats}. The performance of cloud filtering by \cite{rekha2012potential} seems comparable with the regression approach described in this report, albeit they risk rejecting more than 50\% of the clear cases.

>>>>

Figure~\ref{fig:correction:c34-42:thinned} shows the results when the filtered cloudy cases are corrected. Various metrics from the corrected measurements are also shown in Table~\ref{tab:correction:stats}. When cloudy measurements are filtered with noise-threshold = 1$\sigma$, around 14\% cases of the thinned dataset are classified as cloudy and the average deviation in the corrected dataset is -0.069 K. Whereas, with noise-threshold= 2$\sigma$, only 9\% are classfied as cloudy and the average deviation is -0.117 K. This indicates that a larger value of noise threshold can incorrectly classify some cloudy cases as clear.

\begin{table}[!bt]
	\centering
	\begin{tabular}[b]{c|c|c|c}
		 Dataset & Bias & Standard & Measure\\
		 		 & [K] & deviation[K] & skewness [K]\\	
		\hline
		noise & 0.006& 0.628& -0.006\\
		all& -0.818& 4.699& -10.385\\
		thinned& -0.465& 1.556& -5.007\\
		$1\sigma$& -0.069& 0.904& -2.543\\
		$2\sigma$& -0.117& 0.903& -2.597\\
		sreerekha et al& -0.181& 0.731& -0.506\\
		\hline
	\end{tabular}
	\caption{Various metrics for different subsets of the measurement dataset. The different datasets are: noise(simulation dataset),  All (all measurements are considered), thinned (50\% of clear sky measurements are removed), $1\sigma$ (cloudy measurements are filtered with noise-threshold = 1$\sigma$), $2\sigma$ (cloudy measurements are filtered with noise-threshold = 2$\sigma$), sreerekha (measurements are filtered according to criteria described in \cite{rekha2012potential})   }
	\label{tab:correction:stats}
\end{table}
%
In past, \cite{rekha2012potential} have highlighted the applicability of 229 GHz channel to identify the ice clouds. In the report, they use 229 GHz (channel-4x) to identify the ice clouds in 183.31$\pm$7 GHz. In their approach, all cases with TB difference between 229 Ghz and 183.31$\pm$7 GHz greater than 4 K as classified as cloudy. This information can be used to filter out the cloudy cases in all other 183 GHz channels. No correction is provided to the cloudy cases. In order to compare the performance of the correction scheme described here, the filtering scheme by \cite{rekha2012potential} is used a reference. The results from approach are also shown in Figure\ref{fig:correction} and Table~\ref{tab:correction:stats}. The performance of cloud filtering by \cite{rekha2012potential} seems comparable with the regression approach described in this report, albeit they risk rejecting more than 50\% of the clear cases.
